---
output:
  pdf_document: default
  html_document: default
---
Tables: AMS, DAS, DAS2 

Location: Sole

Schema: AMS, DAS, DAS2

## Overview
These are the three schema that track Allocations.  DAS was the initial schema. Then came DAS2. DAS2 begat AMS.

## Changes to Collections Methods

## Tips `n Tricks

## General Caveats


## Sample Projects

## Update Frequency and Completeness


## Other Metadata sources
+ INPORT.  https://inport.nmfs.noaa.gov/inport/item/11773
+ NEFSC's Data Dictionary  http://nova.nefsc.noaa.gov/datadict/


## Related Tables

## Support Tables

```{r amsunique , tab.cap="Unique  fields \\label{amsunique}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r amsprimary, tab.cap="Primary Source fields -  These fields are firsthand data. \\label{amsprimary}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r amssecondary, tab.cap="Secondary Source Fields. These fields might be more accurate somewhere else.  \\label{amssecondary}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r amsQAQC, tab.cap="QAQC columns. Quality Control or Auditing fields.  \\label{amsQAQC}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

