---
output:
  pdf_document: default
  html_document: default
---
Tables: MORT_ELIG_CRITERIA

Location: Sole

Schema: MQRS

## Overview
The MQRS system is fun.

The SECTOR tables are in the MQRS schema, but they are special enough to warrant their own entry.
       
        
## Current Collection Methods

## Changes to Collections Methods

## Tips `n Tricks

## General Caveats
* There is an APP_NUM. This is different from the AP_NUM in the PERMIT system.

* There are business names. They do not necessarily match the business names from the permit system. 

## Sample Projects

## Update Frequency and Completeness


## Other Metadata sources
+ INPORT.  https://inport.nmfs.noaa.gov/inport/item/12987
+ Missing from NEFSC's Data Dictionary  http://nova.nefsc.noaa.gov/datadict/


## Related Tables
+ BUS_OWN contains ownership data that is often linked to these PERMIT data. We'll put them in a separate section.
+ CPH
+ OPERATORS (captains) are permitted independently 
## Support Tables
  + VALID_FISHERY translates the PLAN and CAT into words.

```{r MQRSunique , tab.cap="Unique  fields \\label{MQRSunique}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r MQRSprimary, tab.cap="Primary Source fields -  These fields are firsthand data. \\label{MQRSprimary}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r MQRSsecondary, tab.cap="Secondary Source Fields. These fields might be more accurate somewhere else.  \\label{MQRSsecondary}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r MQRSQAQC, tab.cap="QAQC columns. Quality Control or Auditing fields.  \\label{MQRSQAQC}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

