---
output:
  pdf_document: default
  html_document: default
---
Tables: MORT_ELIG_CRITERIA, SECTOR_YEAR_ROSTER


Location: Sole

Schema: MQRS

## Overview
The MQRS system is fun. It contains information on "eligibilities."  The sector rosters are also stored here.  It is used in conjunction with other tables, but not cross-referenced against them for logical consistency.
        
## Current Collection Methods
Someone at GARFO puts data into the MQRS databases.

## Changes to Collections Methods

## Tips `n Tricks

## General Caveats

  *  The sector rosters are stored in "SECTOR_YEAR_ROSTERS."  These contain a sector_id, year, and MRI (among other things.)  There are also "views" (SECTOR_PARTICIPANTS_CPHYYYY and SECTOR_PARTICIPANTS_NO_CPHYYYY).  These link the MRI to the PERMIT. Unfortunately, they are all broken as of April 18, 2018. They are broken because the underyling code does not properly check dates when it links the MRI to a permit.  Here is code that will illustrate:
    
  1. MRI 1755 should link to permit 100598 any time between april 26, 1994 and june 17, 2015
  
```
select per_num, vessel, owner, date_eligible, date_cancelled, right_id, auth_id
from mqrs.mort_elig_criteria where right_id=1755 order by  date_eligible;
```

 2.  None of these do that properly:
 
```
select * from mqrs.sector_participants_CPH where mri=1755;
select * from mqrs.sector_participants_CPH2011 where mri=1755;
select * from mqrs.sector_participants_CPH2011 where mri=1755;
```


This is happening in part because the underlying code forgot to screen for valid dates.


  * There is an APP_NUM. This is different from the AP_NUM in the PERMIT system.

  * There are business names. They do not necessarily match the business names from the permit system. 

  * History Retention and CPH are essentially synonyms. 
  
  * When an owner puts a right into CPH, the last known PER_NUM associated with that RIGHT_ID is stored.  

> we don't change the relationship between the CPH and the permit if a new owner or the same owner places a new set of permits on the vessel.  The CPH records remain as is until they are moved to another vessel.  We place the permits in CPH based on the last known or permitted vessel. [Ted Hawes @ GARFO, April 18, 2018]  

This can create PER_NUMs with more than 1 RIGHT_ID. Ted Hawes suggests adding
```
auth_type not in ('CPH','HISTORY RETENTION')
```
and then 
```
auth_type  in ('CPH','HISTORY RETENTION')
```
And stitching results together with a union.


  * Sometimes an entry gets put into the MQRS database where the DATE_ELIGIBLE is equal to the DATE_CANCELLED. This may cause mis-merges.  You also may want to exclude these completely from your query.
  
  ```
select * from mqrs.mort_elig_criteria
  where date_eligible<>date_cancelled or date_cancelled is null;
```
  * There was a "cleanup" in 2009.  [Ted Hawes]

  * Auth_id is really only used internally.  auth_id is a unique field for each transaction, and from the original creators of this system back in the early 1990s, the auth_id authorizes the issuance of a permit to the vessel or it authorizes allocation to be issued to the vessel.  The idea was that the auth_id would be used to connect the permit system with mort_elig_critieria when the permit staff processes an application for a limited access permit.  MQRS will authorize the issuance of a limited access using the auth_id. [Ted Hawes]
  
  * The auth_id and right_id can be the same when a new limited access permit is created. Alternatively, when auth_id=right_id, the right has never been transferred.[Ted Hawes]
  
  
  * There are at least a handful of cases in which a different system (DAS, DAS2 mostly) links to an incorrect right id. For example: 
  ```
select * from DAS.DAS_ALLOCATION where right_to_days_id not in (select distinct right_id from MQRS.mort_elig_criteria where fishery='MULTISPECIES') and das_category='A';  
```
will extract all the entries in the DAS.DAS_ALLOCATION table that have an MRI that is not in the MQRS.mort_elig_criteria.  This shouldn't be possible, because an entity needs an MRI 

similarly:
```
select distinct right_id  from das2.allocation where plan='MUL' and 
right_id not in (select distinct right_id from mort_elig_criteria where fishery='MULTISPECIES')
```

## Sample Projects

## Update Frequency and Completeness


## Other Metadata sources
+ INPORT.  https://inport.nmfs.noaa.gov/inport/item/12987
+ Missing from NEFSC's Data Dictionary  http://nova.nefsc.noaa.gov/datadict/


## Related Tables
+ BUS_OWN contains ownership data that is often linked to these PERMIT data. We'll put them in a separate section.
+ CPH
+ OPERATORS (captains) are permitted independently 

## Support Tables
  + VALID_FISHERY translates the PLAN and CAT into words.

```{r MQRSunique , tab.cap="Unique  fields \\label{MQRSunique}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r MQRSprimary, tab.cap="Primary Source fields -  These fields are firsthand data. \\label{MQRSprimary}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r MQRSsecondary, tab.cap="Secondary Source Fields. These fields might be more accurate somewhere else.  \\label{MQRSsecondary}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r MQRSQAQC, tab.cap="QAQC columns. Quality Control or Auditing fields.  \\label{MQRSQAQC}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

