---
output:
  pdf_document: default
  html_document: default
---
Tables: VPS_VESSEL; VPS_FISHERY_NER 

Location: Sole

Schema: PERMIT

## Overview
The permit data contain information about fishing vessels, the fisheries they can participate in. These data are generated through permit applications that are submitted to GARFO by vessel owners.  

+ VPS_VESSEL
+ VPS_FISHERY_NER
+ BUS_OWN
+ VPS_OWNER
        
## Current Collection Methods

## Changes to Collections Methods

## Tips `n Tricks

## General Caveats
* There is an AP_NUM. This is different from the APP_NUM in the MQRS system.

* The same permit number does not necessarily link to the same vessel through all years, as vessels may be upgraded or replaces. 

* The same permit number does not necessarily link to the same owner over time, as vessels (with accompanying permits) can be sold.

* The are 5 date fields in VPS_FISHERY_NER  

* There have been "clean ups" -- sometimes an entry gets put into VPS_VESSEL where the DATE_ISSUED is equal to the DATE_CANCELED. This may cause mis-merges.  You also may want to exclude these completely from your query.
```
select * from vps_vessel where (date_issued<>date_canceled or date_canceled is null);
```

* Similarly, you may  want to exclude rows where start_date >=end_date or start_date>=date_expired 
 
*  BUS_OWN and VPS_OWNER are used to aggregate multi-vessel firms together for Regulatory Flexibility Act Analysis. 

* Scallop and Groundfish "ownership" has been databased going back to 1996 (OWNER_HISTORY_PIDS). Not exactly relevant, but could track "income" or something else at the firm level for a sbuset of those two fisheries. Be careful when thinking about 

## Sample Projects

## Update Frequency and Completeness


## Other Metadata sources
+ INPORT.  https://inport.nmfs.noaa.gov/inport/item/12985
+ NEFSC's Data Dictionary  http://nova.nefsc.noaa.gov/datadict/


## Related Tables
+ BUS_OWN contains ownership data that is often linked to these PERMIT data. We'll put them in a separate section.
+ MQRS tracks the ability of a *thing* to participate in a moratorium fishery. We'll put them in a separate section.  Allocations are tracked in other places (DAS, DAS2, and AMS).
+ CPH
+ OPERATORS (captains) are permitted independently 




## Support Tables
  + VALID_FISHERY translates the PLAN and CAT into words.

```{r vpsunique , tab.cap="Unique  fields \\label{vpsunique}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r vpsprimary, tab.cap="Primary Source fields -  These fields are firsthand data. \\label{vpsprimary}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r vpssecondary, tab.cap="Secondary Source Fields. These fields might be more accurate somewhere else.  \\label{vpssecondary}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r vpsQAQC, tab.cap="QAQC columns. Quality Control or Auditing fields.  \\label{vpsQAQC}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

