---
output:
  pdf_document: default
  html_document: default
---
Tables: VPS_VESSEL; VPS_FISHERY_NER 

Location: Sole

Schema: PERMIT

## Overview
The permit data contain information about fishing vessels, the fisheries they can participate in. These data are generated through permit applications that are submitted to GARFO by vessel owners.  

+ VPS_VESSEL
+ VPS_FISHERY_NER
        
        
## Current Collection Methods

## Changes to Collections Methods

## Tips `n Tricks

## General Caveats
* There is an AP_NUM. This is different from the APP_NUM in the MQRS system.

* The same permit number does not necessarily link to the same vessel through all years, as vessels may be upgraded or replaces. 

* The same permit number does not necessarily link to the same owner over time, as vessels (with accompanying permits) can be sold.


## Sample Projects

## Update Frequency and Completeness


## Other Metadata sources
+ INPORT.  https://inport.nmfs.noaa.gov/inport/item/12985
+ NEFSC's Data Dictionary  http://nova.nefsc.noaa.gov/datadict/


## Related Tables
+ BUS_OWN contains ownership data that is often linked to these PERMIT data. We'll put them in a separate section.
+ MQRS tracks the ability of a *thing* to participate in a moratorium fishery. We'll put them in a separate section.  Allocations are tracked in other places (DAS, DAS2, and AMS).
+ CPH
+ OPERATORS (captains) are permitted independently 
## Support Tables
  + VALID_FISHERY translates the PLAN and CAT into words.

```{r vpsunique , tab.cap="Unique  fields \\label{vpsunique}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r vpsprimary, tab.cap="Primary Source fields -  These fields are firsthand data. \\label{vpsprimary}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r vpssecondary, tab.cap="Secondary Source Fields. These fields might be more accurate somewhere else.  \\label{vpssecondary}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r vpsQAQC, tab.cap="QAQC columns. Quality Control or Auditing fields.  \\label{vpsQAQC}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|	Description
|:---------------	|:--------------------------------------------------------
|	Placeholders	|	
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

