---
output:
  pdf_document: default
  html_document: default
---
Tables: VESLOGyyyyT;  VESLOGyyyyG;  VESLOGyyyyS;  

Location: Sole

Schema: VTR

## Overview
The veslog data contains everything collected through the Vessel Trip Report System.   These data are primarily generated through mandatory reporting by federally-permitted fishing vessels.

+ 1994 to present
+ one table per year
        
        
## Current Collection Methods
These data are the result of mandatory federal vessel reporting.  Federally permitted vessels are required to submit one VTR report per "gear-mesh-area" fished. 50CFR648.7(b)(1).

## Changes to Collections Methods
+ The VTR form has changed slightly over time.  You can get the VTR form, with instructions at https://www.greateratlantic.fisheries.noaa.gov/aps/evtr/vtr_inst.pdf

+ Electronic VTRs start in 2011.

+ Some fisheries allow for (or require) reporting through a different system.

## Tips `n Tricks.
+ A dealer-veslog link can be made reasonbly well starting in 2005.  To make this link, match the the CFDBS.VTRSERNO to VESLOG.SERIAL_NUM.  Chances are that you care about Trip-level outcomes: be careful, because a vessel may have more than one SERIAL_NUM per TRIPID in the VESLOG tables.
+ Vessels may declare out of fishing.  The NOT_FISHED column in VESLOG_T can be used to filter these out.   
+ The TRIPID is unique to a "fishing trip." 
    * A TRIPID to should match to at least one GEARID.
    * A TRIPID to should match to at least one CATCH_ID (if a vessel caught any fish)
    * The NRPAGES and NSUBTRIP Columns will be something other than ```1``` if there are more than one GEARID corresponding to a particular TRIPID. 
+ The GEARID is unique to the "gear-mesh-area" fished. There should be a one-to-one correspondence between GEARID and SERIAL_NUM.  
    * A GEARID to should match to exactly 1 TRIPID
    * A GEARID to could match to 0 CATCH_ID if no fish was caught.
    * A GEARID is far more likely to match to 1 or more CATCH_IDs though.
+ The CATCH_ID is unique to the "SPPCODE- DEALNUM-dealer-gearcode-mesh-area" fished.
    * A CATCH_ID to should match to at exactly 1 GEARID. And therefore exactly 1 TRIPID).
+ DATESAIL, DATELND1, DATELND2 include clock time.  You can sometimes get negative trip durations due to reporting or data entry errors.

## General Caveats.
* 1994-1995 are kind of sketchy

* Electronic VTRs have very long SERIAL_NUM, TRIPID, GEARID, and CATCH_ID.  Some software doesn't like this (Excel, stata) -- you might want to do this:```select to_char(g.serial_num) from veslog2014g g```
    
* Some of the older numbers (from 1994-1995) are non-numeric. 
    
* All quanties are "Hail Weights," which are the operator's best estimate of catch.
* SPPCODES will not match well to dealer's  NESPP4 codes. For example, VTR cod is all 0818 (unclassifed round). Almost all Cod will eventually be classified when sold; there is very little 0818 in dealer data.

* The following species are sketchy:

    + Surfclam and Ocean Quahog dealer reports are contained in the SFCLAM schema (separate from CFDBS).  It is unclear whether reports of SC and OQ in CFDETS and CFDERS are duplicates or not, particularly for landings of Maine Mahogany Clam [Walden].

    + Giant Bluefin Tuna dealer are supposed to be reported individually and should be in a different schema.  Giant Bluefin Tuna in CFDERS are either misreporting or duplication [George Silva, NMFS HMS].

* PORTLND1 and PORTLND2 are inconsistently encoded over time. 
    + The names corresponding to the port codes may or may not match to Census “units.”  The 2 digit state code does not correspond to FIPS codes.  
    + The PORTLND1 and PORTLND2 fields are data entered and error-corrected on the fly[Lee, Dentremont]  This means that data entry of ```NEW ROCHELL, NY``` is autocorrected to ```NEW ROCHELLE, NY``` and coded as ```PORT=350739```
    + This might provide more insight:```select * from vtr.vlportsyn order by doc desc;```
    
* CAREA, CNEMAREA, CLATDEG, CLATMIN, CLATSEC, CLONDEG, CLONMIN, CLONSEC, CERRNO, AREA_IND, TENMSQ
    + The "C" stands for calculated.  The calculation is pretty complicated. [Lee, H. McBride]
    + The "AREA" refers to the Northeast region statistical areas.
        + AREA in the 300s and 400s are in Canada
        + AREAS under 200 are Inshore. They shouldn't show up, but occasionally do.
    + "NEMAREA" includes "inshore areas"
        + The latitude and longitude points reported on a VTR are first binned into a Ten Minute Square, then checked against a lookup table that converts Ten Minutes Squares into statistical areas [LOC2AREAS]. 
        + If there is a match, then the reported latitude and longitude points are accepted.
        + If there is no match and the reported lat-lon is in an AREA adjacent to the reported AREA, then the lat-lon points are accepted and the reported statistical area is replaced by the AREA corresponding to the lat-lon.
        + If there is no match and the reported lat-lon is *not* in an AREA adjacent to the reported AREA, then the lat-lon points are rejected and converted to ```NULL``` values. The reported statistical area used as the CAREA.  
    + Technically, only degrees and minutes are required to reported.
    + Some vessels report LORAN readings. These are converted to lat-lon prior to that entire process.
    + This QAQC step is performed differently in the GARFO CATCH, IMAGES, DOCUMENT data.

* Some dealer numbers (DNUM in VESLOG_S) indicate that catch was not sold to a federally permitted dealer (DNUM<=8 or DNUM=99998)
* Recreational trips report numbers of fish, not pounds.
* PORTLND1 and PORTLND2 are recorded. Sailing port is not recorded
    + Use landing location from previous trip?
    + Assume round trip to same port?
* The code for WOLFFISH is CAT.  The code for BLUE CATFISH and NS Catfish are CATB and CATNS respectively. This is hilarious.  If you need to pick WOLF apart from CATFISH, wolffish is not caught inshore.
* The  code for WHITE HAKE is WHAK. White HAKE is not Whiting. Sometimes operators write "WHAK" for "WHITING - HAKE."  They should be writing SHAK, HAKOS, or WHB.   You can separate based on mesh size if necessary. [Thunberg]



## Sample Projects 

## Update Frequency and Completeness 
+ Nightly updates. Expect approximately 300 changes or additions to the current and previous year of data per day.
+ Data is “complete” 6-9 months after the end of the calendar year; however, small changes are always occurring.

## Other Metadata sources
+ INPORT.  https://inport.nmfs.noaa.gov/inport/item/1423
+ NEFSC's Data Dictionary  http://nova.nefsc.noaa.gov/datadict/

+ Preceded by: "none"
+ Succeeded by: n/a

## Related Tables very incomplete.
+ CATCH, IMAGES, DOCUMENT - these are the "GARFO" version of VTR. C,I,D are a single table, not one per year.  I can't even.

## Support Tables very incomplete.
+ VLSPPTBL decodes SPPCODES into names and NESPP4 codes. So does VLSPPSYN_94_95, which looks deprecated.    
+ TENMINSQ, LOC,LOC2AREAS
+ PORTSYN, VLPORTSYN
+ VLGEAR - decodes gear codes into english

```{r veslog unique , tab.cap="Fields in VESLOG  \\label{veslog_unique}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|Location | 	Description
|:---------------		|:---------- |:----------------------------------
CAREA	|		G		|
CATCH_ID	|			S	|
CLATDEG	|		G		|
CLATMIN	|		G		|
CLATSEC	|		G		|
CLONDEG	|		G		|
CLONMIN	|		G		|
CLONSEC	|		G		|
CNEMAREA	|		G		|
CREW	|	T			|
DATE_SIGNED	|	T			|
DATELND1	|	T			| This includes  time
DATELND2	|	T			| This includes  time
DATESAIL	|	T			| This includes  time
DATESOLD	|			S	| 
DEALNAME	|			S	|
DEALNUM	|			S	|
DEPTH	|		G		|
FZONE	|		G		|
GEARCODE	|		G		|
GEARID	|		G	S	|
GEARQTY	|		G		|
GEARSIZE	|		G		|
HULLNUM	|	T			|
MESH	|		G		|
NANGLERS	|	T			|
NHAUL	|		G		|
NOT_FISHED	|	T			|
NRPAGES	|	T			|
NSUBTRIP	|	T			|
OPERATOR	|	T			|
OPERNUM	|	T			|
PAGENO	|		G		|
PERMIT	|	T			|
PORT	|	T			|
PORTLND1	|	T			|
PORTLND2	|	T			|
QDSQ	|		G		|
QTYDISC	|			S	|
QTYKEPT	|			S	|
SERIAL_NUM	|		G		|
SOAKHRS	|		G		|
SOAKMIN	|		G		|
SPPCODE	|			S	|
STATE1	|	T			|
STATE2	|	T			|
SUBTRIP	|		G		|
TENMSQ	|		G		|
TIMELND1	|	T			|
TIMELND2	|	T			|
TIMESAIL	|	T			|
TRIP_ACTIVITY_TYPE	|	T			|
TRIPCATG	|	T			|
TRIPID	|	T	G	S	|
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r veslog primary, tab.cap="Primary Source fields -  These fields might be useful for linking, either exactly or fuzzy. \\label{veslog_primary}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|Location | 	Description
|:---------------		|:---------- |:----------------------------------
DATELND1	|	T			|
DATELND2	|	T			|
DATESAIL	|	T			|
DATESOLD	|			S	|
DEALNAME	|			S	|
DEALNUM	|			S	|
HULLNUM	|	T			|
TIMELND1	|	T			|
TIMELND2	|	T			|
TIMESAIL	|	T			|
PERMIT	|	T			|
PORT	|	T			|
PORTLND1	|	T			|
PORTLND2	|	T			|
SERIAL_NUM	|		G		|
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

```{r veslog QAQC, tab.cap="QA/QC columns. Quality Control or Auditing fields.  \\label{veslog_QAQC}", echo=FALSE, message=FALSE, warnings=FALSE, results='asis'}
tabl <- "
|	Column	|Location | 	Description
|:---------------		|:---------- |:----------------------------------
AREA_IND	|		G		|
BATCHID	|	T		S	|
DATE_RECV	|		G		|
DC	|	T	G	S	|
DE	|	T	G	S	|
FILENAME	|		G		|
IMG_DATE	|		G		|
IMGTYPE	|		G		|
UC	|	T	G	S	|
UE	|	T	G	S	|
SIDEID	|		G		|
"
cat(tabl) # output the table in a format good for HTML/PDF/docx conversion
```

